Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-07-06 write-ups/FSE/paper.tex
This is such a good paper.

Cooperative kernels are written using the following
extensions: $\transmit$, a qualifier on the variables of a
thread; $\offerkill$ and $\offerfork$, the key functions that enable
cooperative scheduling; and $\globalbarrier$ and $\mathsf{resizing\_global\_}$ $\mathsf{barrier}$
%$\resizingglobalbarrier$
primitives for inter-workgroup synchronisation.

>>>>

Cooperative kernels are written using the following
extensions: $\transmit$, a qualifier on the variables of a
thread; $\offerkill$ and $\offerfork$, the key functions that enable
cooperative scheduling; and $\globalbarrier$ and $\mathsf{resizing\_global\_barrier}$
%$\resizingglobalbarrier$
primitives for inter-workgroup synchronisation.
